An Efficient E-field Parallel Imaging Calibration Algorithm for Next-Generation Radio Telescopes

### 2016-01-25 cal_demo/ms.tex
Adding data text to cal demo

\section{Application to LWA data}\label{sec:data}
Reference for Cyg-A: \citealt{coh07}. Ref for Cas-A: \citealt{kas07}.
Apply to LWA data.

@@

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.3\linewidth]{figures/cal_paper_data_image_before.pdf}
\includegraphics[width=0.3\linewidth]{figures/cal_paper_data_image_after.pdf}
\includegraphics[width=0.3\linewidth]{figures/cal_paper_gsm_beam_weighted.pdf}
\caption{\textcolor{red}{caption!}}
\label{fig:data_images}
\end{center}
\end{figure*}

>>>>

\section{Application to LWA data}\label{sec:data}
We next demonstrate our calibration algorithm using an observation from the LWA station in New Mexico. The data is from the LWA narrow-band transient buffer (TBN), with time ordered voltage data from 255 antennas within a core radius of 100~m. The central frequency is 74.03 MHz, and a bandwidth of 100 kHz and writeout timescale of 5.12 ms (frequency channel resolution of 195.3125 Hz). For this demonstration we limit ourselves to a single polarization.

After correcting for geometric cable delays, the instrument is naturally well calibrated, as was seen in the demonstration of the EPIC imager in \citealt{thy15c}. However, we will aim to improve yet on this calibration using our algorithm.

We proceed by forming model visibilities. We model only two bright objects as point sources: Cyg A with flux 16611.68 Jy \citep{coh07}; and Cas A with flux 17693.9 Jy \citep{kas07}. Because the raw data is attenuated by the primary beam of the instrument, we also account for this in our model using beam values consistent with \cite{hic12}.

We made several choices while studying the behavior of the LWA data to improve our calibration. We inspected the amplitudes of the voltages to be roughly consistent with average gain amplitudes of 0.25, so we initialized our gains at this level to allow the calibration to converge quickly. We also found a boost in signal to noise is achieved easily by averaging frequency channels and assuming the gains are constant within a sub-band. Here we average solutions across 150 channels, or about 29 kHz. With a fractional bandwidth $B/f_0 = 3.9 \times 10^{-4}$, we felt safe assuming a smooth bandpass. Because there is still a fair amount of noise in the data, a damping factor of $\gamma = 0.7$ was adopted.

Finally, we found that seven antennas\footnote{LWA antenna IDs 48, 85, 124, 148, 203, 217, and 244 were flagged.} produced unstable gain solutions, and in fact corrupted the ensemble. We therefore flagged these antennas for our analysis, resulting in a total of 248 antennas to calibrate. In each calibration loop, we form our feedback correlations and update our gain estimates over 10 timestamps (51.2 ms). We iterate the loop 30 times for a total of 1.536 seconds. The results of this experiment are shown in figures~\ref{fig:data_phase}~--~\ref{fig:data_images}.

Figure~\ref{fig:data_phase} shows the phase of our gain estimates over our 30 calibration iterations, again with each colored line representing a different antenna. Given the quality of uncalibrated image demonstrated in \cite{thy15c}, it is a bit surprising to see the phase variation in our solutions. However, the phases are relatively flat after about 15 iterations (modulo noise), and exhibit a central ``trunk" where the majority of phases are congregated. This behavior is suggestive that while the uncalibrated voltages were able to produce a viable image, the minor changes from our solutions will focus the image and improve the quality. The actual location of the ``trunk" (slightly negative) is simply determined by the reference antenna chosen to have identically zero phase, but happens to be slightly more positive than the bulk of antennas. We also note that some phases appear to exceed $\pm \pi$ radians, this is due to the unwrapping done for plotting clarity.

@@

The gain amplitudes as a function of calibration iteration are shown in figure~\ref{fig:data_amp}. There is a fairly wide range in gain amplitudes (from 0.12 to 0.59). However, this is not surprising due to the non-uniformity in the cables from the antennas to the receivers. Again, the amplitudes are noisy by relatively flat.

@@

Figure~\ref{fig:data_images} shows the improvement in the images due to our calibration. The left panel shows the uncalibrated image integrated over 51.2 ms, 29 kHz. Cyg~A is prominent near the center of the image, and Cas~A is also clearly visible in the upper right. The middle panel shows the image produced after calibration with identical integration time and bandwidth. The sidelobes throughout the image are significantly suppressed, and the galactic plane is much more evident. We also note that the feature just to the right of Cyg~A is dimmer in the calibrated image, better matching the expected flux from the global sky model (GSM, \citealt{deo08}). We show the GSM modulated by two factors of the LWA primary beam in the right panel of figure~\ref{fig:data_images} for reference.

\begin{figure*}
\begin{center}
\includegraphics[width=0.33\linewidth]{figures/cal_paper_data_image_before.pdf}
\includegraphics[width=0.33\linewidth]{figures/cal_paper_data_image_after.pdf}
\includegraphics[width=0.33\linewidth]{figures/cal_paper_gsm_beam_weighted.pdf}
\caption{\textcolor{red}{caption!}}
\label{fig:data_images}
\end{center}
\end{figure*}

To compare the image qualities quantitatively we compute the dynamic range, defined as the peak of the image over the noise level. We estimate the noise level as the median of the absolute deviation of the image. With this metric we find the calibrated image to have a 55\% dynamic range improvement over the uncalibrated image.
